### 2011-05-10 paper.tex
outline of amplification section

\newcommand{\bp}{\textsf{BP}}
\newcommand{\strongbp}{\textsf{strongBP}}
\newcommand{\parity}{\oplus}
\newcommand{\p}{\textsf{P}}

@@

>>>>

\newcommand{\bp}{\textsf{BP}}
\newcommand{\strongbp}{\textsf{strongBP}}
\newcommand{\parity}{\oplus}
\newcommand{\p}{\textsf{P}}
\newcommand{\op}{\textsf{Op}}

@@

The aim of this section is to prove the following amplification result:

\begin{theorem}\label{amplify}
Let $C$ be a \emph{$\{\Sigma,\Pi,\bp,\parity\}$}-constructible complexity class. Then \emph{$\bp \cdot C = \strongbp \cdot C$}.
\end{theorem}
A proof of this theorem is immediate by induction from the following two lemmas:

\begin{lemma}\label{majorityimpliesamplify}
If $C$ is a complexity class which is closed under majority reductions, then\linebreak \emph{$\bp \cdot C = \strongbp \cdot C$.}
\end{lemma}

\begin{lemma}\label{ampliftymainlemma}
Let $C$ be a \emph{$\{\Sigma,\Pi,\bp,\parity\}$}-constructible complexity class. If $C$ is closed under majority reductions, then (i) \emph{$\Sigma \cdot C$}, (ii) \emph{$\Pi \cdot C$}, (iii) \emph{$\bp \cdot C$}, and (iv) \emph{$\parity \cdot C$} are all closed under majority reductions.
\end{lemma}
